Two NIRCam channels are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-10-04 ms.tex

\subsection{Readout Considerations}\label{sec:readout}

NIRCam's detectors have numerous pixel readout schemes that factor into saturation limits and SNR calculations for a given observation.
%JWST's NIRCam instrument has many different possible readout patterns per pixel and array that all factor in to the SNRs and saturation limits for an observation.
We adopt the following nomenclature for the readout (Figure~\ref{fig:readout}):\ an \emph{integration} (also commonly refered to as a ``ramp'') consists of a pixel-reset frame followed by one or more groups of non-destructive reads to sample the pixels' charge accumulation. An \emph{exposure} is considered to be a collection of multiple integrations of the same type and length. Finally, an \emph{observation} consists of many exposures.

%an \emph{observation} consists of one of more exposures which are combined into a single \texttt{FITS} file per exposure.
%Within an exposure, there are one or more integrations, which consist of a reset frame followed by one or more groups of non-destructive reads up a ramp illustrated in Figure~\ref{fig:readout}.

>>>>

\subsection{Readout Considerations}\label{sec:readout}
NIRCam's detectors have numerous pixel readout schemes that factor into saturation limits and SNR calculations for a given observation.
We adopt the following nomenclature for the readout (Figure~\ref{fig:readout}):\ an \emph{integration} (also commonly refered to as a ``ramp'') consists of a pixel-reset frame followed by one or more groups of non-destructive reads to sample the pixels' charge accumulation. An \emph{exposure} is considered to be a collection of multiple integrations of the same type and length. Finally, an \emph{observation} consists of many exposures.
